Quantum Interval-Valued Probability: Contextuality and the Born Rule

### 2017-09-17 prop_letter.tex
prop_letter.tex \section{Gleason} Updating...

While the finite-precision extension of Kochen-Specker theorem asserts
the non-existence of certain kind of QIVPMs, we also want to understand
what a QIVPM could be when it exists. In Sec.~\ref{sec:Interval-Uncertainty},
the only non-trivial QIVPM~ $\bar{\mu}_{3}$ is induced by the quantum
probability measure~$\mu_{1}$ defined in Sec.~\ref{sec:fuzzy}.
This result will first be generalized in this section, and then we
will show some QIVPMs may not be induced by any quantum probability
measure, i.e., no state is consistent with these kind of QIVPMs, while
a quantum probability measure is always induced by an unique state
by Gleason's theorem.

The quantum probability measure~$\mu_{1}$ maps some projectors to
$0$ or $0.5$, which are replaced by $\left[0,0\right]$ or $\left[0.5,0.5\right]$
to get $\bar{\mu}_{3}$. Replacing numbers by intervals containing
them can be generalized if we carefully pick a set of intervals and
a rule to select the correct interval when intervals are overlapping.
For example, consider the following collection of intervals: 
\begin{eqnarray}
\mathscr{I}_{n} & = & \set{\left[\tfrac{k-1}{2n},\tfrac{k+1}{2n}\right]\cap\left[0,1\right]}{k=0,\ldots,2n}\nonumber \\
 &  & \cup\{\imposs,\necess\}
\end{eqnarray}
which are overlapping intervals with length~$1/n$ except the intervals
with length~$\left(2n\right)^{-1}$ at each end. Since these intervals~$[\ell,r]$
are overlapping, we define the non-overlapping interior part of a
interval, $\textrm{Int}\left([\ell,r]\right)$, as in Table~\ref{tab:I2}.
\begin{table}
\caption{\label{tab:I2}Intervals in $\mathscr{I}_{n}$ and their interior
with an concrete example for $\mathscr{I}_{2}$. Although intervals~$[\ell,r]$
are overlapping, their interior~$\textrm{Int}\left([\ell,r]\right)$
are non-overlapping.}

>>>>

While the finite-precision extension of Kochen-Specker theorem asserts
the non-existence of certain kind of QIVPMs, we also want to understand
what a QIVPM could be when it exists. In Sec.~\ref{sec:Interval-Uncertainty},
the only non-trivial QIVPM~ $\bar{\mu}_{3}$ is induced by the quantum
probability measure~$\mu_{1}$ defined in Sec.~\ref{sec:fuzzy}.
This result will first be generalized in this section, and then we
will show some QIVPMs may not be induced by any quantum probability
measure, i.e., no state is consistent with these kind of QIVPMs, while
there is always an unique state consistent with a quantum probability
measure by Gleason's theorem.

The quantum probability measure~$\mu_{1}$ maps some projectors to
$0$ or $0.5$, which are replaced by $\left[0,0\right]$ or $\left[0.5,0.5\right]$
to get $\bar{\mu}_{3}$. Replacing numbers by intervals containing
them can be generalized if we carefully pick a set of intervals and
a rule to select the correct interval when intervals are overlapping.
For example, consider the following collection of intervals: 
\begin{equation}
\begin{aligned}\mathscr{I}_{n}= & \set{\left[\tfrac{k-1}{2n},\tfrac{k+1}{2n}\right]\cap\left[0,1\right]}{k=0,\ldots,2n}\\
 & \cup\{\imposs,\necess\}
\end{aligned}
\end{equation}
which are overlapping intervals with length~$1/n$ except the intervals
with length~$\left(2n\right)^{-1}$ at each end. Since these intervals~$[\ell,r]$
are overlapping, we define the non-overlapping interior part of a
interval, $\textrm{Int}\left([\ell,r]\right)$, as in Table~\ref{tab:I2}.
\begin{table}
\caption{\label{tab:I2}Intervals in $\mathscr{I}_{n}$ and their interior
with an concrete example for $\mathscr{I}_{2}$. Although intervals~$[\ell,r]$
are overlapping, their interior~$\textrm{Int}\left([\ell,r]\right)$
are non-overlapping.}
